Fasano--Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2021-06-17 journalMS/article.tex
added benchmarking method info

%% recommended packages
\usepackage{thumbpdf,lmodern}
\usepackage{amssymb}

@@

\hyphenation{Fa-sa-no=Fran-ces-chi-ni}

@@

To assess the computational efficiency, we benchmarked the package as follows.
\RBnote{Please explain the benchmark here; make note also of the specs of the machine that was used,
inc # cores, processor speed, memory, and OS.}
The main distinction between the Peacock and Fasano--Franceschini
tests is in computational efficiency, with  Fasano--Franceschini
scaling as $O(n^2)$ relative to Peacock's complexity of  $O(n^3)$
\citep{Lopes2007}.  Our benchmarks also show this advantage, as shown
in \textbf{Figure~\ref{fig:bmark}A}.  While the implentation of the
bootstrapping procedure increases runtime in comparison to the
approximate fit from  \citet{numericalRecipes}, parallelization of the
Fasano--Franceschini test shows a four-fold reduction in run time when
parallelized across 8 cores. \textbf{Figure~\ref{fig:bmark}B}.
% (See the \pkg{Peacock.test} package for \proglang{R} implementation of the Peacock test.)

>>>>

%% recommended packages
\usepackage{thumbpdf,lmodern}
\usepackage{amssymb}
\usepackage{amsmath}

@@

%\hyphenation{Fa-sa-no=Fran-ces-chi-ni}

@@

To assess the computational efficiency, we benchmarked the package as follows.
Using the \pkg{rbenchmark} package to evaluate runtime, the Fasano--Franceschini
test and Peacock test were run under four different samples sizes
($n=10, 100, 1000, 5000$), with 10 replicates for each run. The
Fasano--Franceschini test bootstrap precedure was further evaluated
under four different bootstrap iterations (no bootstrap, 10, 100, 1000),
again using 10 replicates for each run. Reported results represent the
average run time of the 10 replicate benchmarks. All benchmark tests were run on a 2018 macBook
Pro Mac (macOS Catalina) with a 2.7-GHz Quad-Core Intel Core i7 processor and 16 GB of 2133 MHz LPDDR3 memory.

The main distinction between the Peacock and Fasano--Franceschini
tests is in computational efficiency, with  Fasano--Franceschini
scaling as $O(n^2)$ relative to Peacock's complexity of  $O(n^3)$
\citep{Lopes2007}.  Our benchmarks also show this advantage, as shown
in \textbf{Figure~\ref{fig:bmark}A}.  While the implentation of the
bootstrapping procedure increases runtime in comparison to the
approximate fit from  \citet{numericalRecipes}, parallelization of the
Fasano--Franceschini test shows a four-fold reduction in run time when
parallelized across 8 cores (\textbf{Figure~\ref{fig:bmark}B}).
% (See the \pkg{Peacock.test} package for \proglang{R} implementation of the Peacock test.)
